---
title: "Ashwin PRP Analysis"
output: html_notebook
---


#Setup

```{r}
#clear environment
graphics.off()
rm(list = ls(all = TRUE))

#Setting up directories
fsep<-.Platform$file.sep;
Dir_Support <- path.expand("~/Brown Dropbox/Ashwin Srinivasan/R_support_scripts") 
Dir_Experiment <- path.expand("~/Brown Dropbox/Ashwin Srinivasan/DimensionSwitch_PRP")
Dir_BDATA<-path.expand("DataAnalysis/Matlab/BEH")


#load libraries
library(data.table)
library(tidyverse)
library(ggplot2)

```


```{r}
#load data
setwd(Dir_Experiment)
setwd(Dir_BDATA)
df <- fread('z/ALLGRAND(EEG,6sessions)/DimensionSwitchPRP_BehP.txt', header=TRUE, fill=TRUE) 

```

Central Q:How does learning shape the geometry and dynamics of task representations during control-demanding behavior? How does separability of task representations relate to the reduction of multitasking costs via training?

Behavioral Qs
- what evidence of learning can we see from the behavioral data? RT, accuracy, etc.
- can we see any evidence of mitigating multitask costs?
- do our behavioral data provide evidence for 1 mulitasking account over the others? (central bottleneck, scheduling)

Data-tied hypotheses (answer the above questions in terms of specific data analyses):
- Accuracy for both items should increase across time
- RT for both items should decrease across time.
  - RT for item 2 should show a more pronounced decrease
- think about feature/dimension switches!


How do we test these hypotheses with the data we have?:

```{r}
#Clean and Recode Data

taskLabels <- c("Low-High", "Odd-Even", "Red-Blue", "Bold-Faint")
stimNumbers <- c("3", "4", "6", "7")
stimColor <- c("red", "red-faint", "blue-faint", "blue")

df[,SOA:= factor(SOA, labels = c("100ms","250ms", "500ms", "750ms", "1000ms"))]
df[,TASKSET_1:= factor(TASKSET_1, labels = taskLabels)]
df[,TASKSET_2:= factor(TASKSET_2, labels = taskLabels)]
df[,STIMPOS_1:= factor(STIMPOS_1, labels = c("Top", "Bottom"))]
df[,STIMPOS_2:= factor(STIMPOS_2, labels = c("Top", "Bottom"))]
df[,FDIM_1:= factor(FDIM_1, labels = c("Number", "Color"))]
df[,FDIM_2:= factor(FDIM_2, labels = c("Number", "Bottom"))]

df[,F_NUMBER_1:= factor(F_NUMBER_1, labels = stimNumbers)]
df[,F_NUMBER_2:= factor(F_NUMBER_2, labels = stimNumbers)]
df[,S1_1:= factor(S1_1, labels = stimNumbers)]
df[,S2_1:= factor(S2_1, labels = stimNumbers)]

df[,F_COLOR_1:= factor(F_COLOR_1, labels = stimColor)]
df[,F_COLOR_2:= factor(F_COLOR_2, labels = stimColor)]
df[,S1_2:= factor(S1_2, labels = stimColor)]
df[,S2_2:= factor(S2_2, labels = stimColor)]

df[,NUMTASK:= factor(NUMTASK, labels = c("single","double"))]

df$SUBID_S <- df$SUBID
df <- transform(df, SUBID = paste0("1",substr(SUBID, 2, 3)))
df[,EXACT_REP:= factor(EXACT_SW, labels = c("exact","diff"))]

df$S1IDc <- paste(df$S1_1, df$S1_2, sep = "_" )
df$S2IDc <- paste(df$S2_1, df$S2_2, sep = "_" )

```

